% !TeX root = ../thuthesis-example.tex

% 中英文摘要和关键字

\begin{abstract}
在 Python 语言中调用 C/C++ 跨语言接口是一种常见的需求。Python 语法便捷、应用丰富，C/C++ 性能优越、靠近底层，二者的结合能带来更高的生产力。Cython 语言在 Python 语法的基础上增加了 C 类型标注，能以极低的性能损失封装 C/C++ 接口，是为 Python 构建 C/C++ 扩展模块的理想选择之一。本文设计并实现了一种从 C/C++ 声明中自动构建 Cython 包装模块的开发工具，CPP2PY，以降低学习和编写 Cython 程序的时间成本。CPP2PY 以 C/C++ 头文件为输入，输出构建脚本、 Cython 包装代码和对应的Python 类型标注文件。它经过了详尽的软件测试，支持的语法特性包括全局变量、宏、枚举、类、结构体、联合、继承、重载和类型别名等。基于 CPP2PY，本文封装了 C 算法库 SuiteSparse 实现的大规模稀疏矩阵Cholesky分解算法，为Python科学计算库SciPy实现了正确而高效的稀疏矩阵分解功能。实验表明，封装后的 Python 接口与直接编写C程序相比性能损失低于5\%。

  % 关键词用“英文逗号”分隔，输出时会自动处理为正确的分隔符
  \thusetup{
    keywords = {Cython, 跨语言接口, 自动化构建工具, 稀疏矩阵 Cholesky 分解 },
  }
\end{abstract}

\begin{abstract*}
It is a common requirement to call C/C++ foreign function interfaces in Python.
Python provides convenient syntax and a thriving open source community, while C/C++
is famous for its superior performance and proximity to the underlying layer. The combination of both can lead to higher productivity. The Cython language adds C type annotations to the Python syntax, which can encapsulate C/C++ interfaces with little performance losses, making it an ideal choice for building C/C++ extension modules for Python. This article designed and implemented a development tool, CPP2PY, that automatically builds Cython wrappers from C/C++ declarations to reduce the cost of learning and writing Cython programs. CPP2PY takes C/C++ header files as input and outputs setup scripts, Cython wrapping codes, and corresponding Python type annotation files. It has undergone sufficient testing and supports syntax features such as global variables, macros, enumerations, classes, structs, unions, inheritance, overloading, type aliases, etc. Based on CPP2PY, we encapsulated the Cholesky decomposition algorithm for large-scale sparse matrixes implemented by SuiteSparse, a C algorithm library, to achieve a correct and efficient sparse matrix decomposition function for Python scientific computing library SciPy. Experiments have shown that the performance loss of the Python interface is less
than 5\% compared to writing C programs directly.

  % Use comma as separator when inputting
  \thusetup{
    keywords* = {Cython, FFI, Automated Build Tool, Sparse Cholesky Decomposition},
  }
\end{abstract*}
